---
title: "Data wrangling for experiment 1: backfire effects"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing the data-frame to demo the code

Note: I developed this code before learning the magic of loops and functions, so the following code is not at all efficient however should create the following data-frames: final and df_recall, which are used in the analysis.

Please also note that the variable 'REG_TRUST_1' 8 participants selected 'don't know' options which were changed to '4' to keep all the datapoints in the variable when used as a numerical scale. All models including this variable need to be checked with and without these 8 responses.

```{r read in df}

#THIS ASSUMES YOU HAVE THE DATA DOWNLOADED AND SAVED INTO THE SAME PROJECT

data <- read.csv("final_responses.csv")

```

```{r libraries}

library(tidyverse)

```

## Exclusions

```{r}

data$Duration..in.seconds. <- as.numeric(data$Duration..in.seconds.)
data$AGE <- as.numeric(data$AGE)

data <- data %>%
  filter(Duration..in.seconds.>270)

data <- data %>%
  filter(AGE>17)

```

## Creating the final dataframe

```{r agree disagree transformations}

#every agree-disagree item on a scale of 1-7

df1 <- data %>%
  data.frame() %>%
  select(ORIENT_1_1, ORIENT_1_2, ORIENT_1_3, ORIENT_1_4, ORIENT_1_5,
         ORIENT_2_1, ORIENT_2_2, ORIENT_2_3, ORIENT_2_4, ORIENT_2_5, MISTRUST_EX_1, MISTRUST_EX_2, MISTRUST_EX_3, MISTRUST_EX_5, MISTRUST_EX_6, COMP_1, COMP_2, COMP_3, COMP_4, BENEV_1, BENEV_2, BENEV_3, BENEV_4, INTEG_1, INTEG_2, INTEG_3, INTEG_4, AD_TRUST_1, AD_TRUST_2, AD_TRUST_4, AD_TRUST_5, SM_TRUST_1, SM_TRUST_2
         )

df1 <- df1 %>%
  select(ORIENT_1_1, ORIENT_1_2, ORIENT_1_3, ORIENT_1_4, ORIENT_1_5,
         ORIENT_2_1, ORIENT_2_2, ORIENT_2_3, ORIENT_2_4, ORIENT_2_5, MISTRUST_EX_1, MISTRUST_EX_2, MISTRUST_EX_3, MISTRUST_EX_5, MISTRUST_EX_6, COMP_1, COMP_2, COMP_3, COMP_4, BENEV_1, BENEV_2, BENEV_3, BENEV_4, INTEG_1, INTEG_2, INTEG_3, INTEG_4, AD_TRUST_1, AD_TRUST_2, AD_TRUST_4, AD_TRUST_5, SM_TRUST_1, SM_TRUST_2) %>%
  mutate_all(~c(1, 2, 3, 4, 5, 6, 7)[match(.x, c("Strongly disagree", 
                                                 "Disagree", "Somewhat disagree",
                                                 "Neither agree nor disagree",
                                                 "Somewhat agree", "Agree",
                                                 "Strongly agree"))])
```


```{r data acceptability likeability agreement}

#data acceptability on a scale of 1 to 7

df2 <- data %>%
  data.frame() %>%
  select(DATA_ACCEPT)

df2 <- df2 %>%
  select(DATA_ACCEPT) %>%
  mutate_all(~c(1, 2, 3, 4, 5, 6, 7)[match(.x, c("Not at all acceptable", "Mostly unacceptable ", "Somewhat unacceptable", "Neither acceptable nor unacceptable", "Somewhat acceptable", "Mostly acceptable", "Completely acceptable "))])

#likability and agreement on scale of 1 to 5 

df3 <- data %>%
  data.frame() %>%
  select(LIKE)

df3 <- df3 %>%
  select(LIKE) %>%
  mutate_all(~c(1, 2, 3, 4, 5)[match(.x, c("Dislike a great deal", "Dislike somewhat","Neither like nor dislike", "Like somewhat", "Like a great deal"
))])

df4 <- data %>%
  data.frame() %>%
  select(AGREE)

df4 <- df4 %>%
  select(AGREE) %>%
  mutate_all(~c(1, 2, 3, 4, 5)[match(.x, c("Completely disagree", "Somewhat disagree", "Neither agree or disagree", "Somewhat agree", "Completely agree"
))])

```

```{r self-target social media use}

#self-target and social media usage on a scale of 1-5

df5 <- data %>%
  data.frame() %>%
  select(SELF_TAR)

df5 <- df5 %>%
  select(SELF_TAR) %>%
  mutate_all(~c(1, 2, 3, 4, 5)[match(.x, c("Not at all targeted at me", "Mostly not targeted ", "Somewhat targeted", "Mostly targeted", "Completely targeted at me" 
))])

df6 <- data %>%
  data.frame() %>%
  select(SM_USE_1, SM_USE_2)

df6 <- df6 %>%
  select(SM_USE_1, SM_USE_2) %>%
  mutate_all(~c(1, 2, 3, 4, 5)[match(.x, c("Never", "Rarely", "slightly often",  "fairly often", "very often"
))])

```

```{r political interest electoral participation}

#political interest (1-4), electoral participation (yes/no)

df7 <- data %>%
  data.frame() %>%
  select(POL_INT)

df7 <- df7 %>%
  select(POL_INT) %>%
  mutate_all(~c(1, 2, 3, 4)[match(.x, c("Not at all interested", "Mostly uninterested", "Somewhat interested", "Very interested"
))])

df8 <- data %>%
  data.frame() %>%
  select(ELECT_PAR_1, ELECT_PAR_2, ELECT_PAR_3, ELECT_PAR_4, ELECT_PAR_5, ELECT_PAR_6)

df8 <- df8 %>%
  select(ELECT_PAR_1, ELECT_PAR_2, ELECT_PAR_3, ELECT_PAR_4, ELECT_PAR_5, ELECT_PAR_6) %>%
  mutate_all(~c(0, 1)[match(.x, c("No, I have not", "Yes, I have"
))])

```

```{r political ideology}

#Political ideology categorical with 8 categories (reduced to 4 for LR)

df9 <- data %>%
  data.frame() %>%
  select(PERC_ID, LEFT_RIGHT)

df9 <- df9 %>%
  select(PERC_ID, LEFT_RIGHT) %>%
  mutate_all(~c(-3, -2, -1, 0, 1, 2, 3)[match(.x, c("Strongly left leaning", "Fairly left leaning", "Slightly left leaning", "Neither left nor right leaning", "Slightly right leaning", "Somewhat right leaning", "Fairly right leaning", "Strongly right leaning"
))])

df9 <- df9 %>% 
  replace_na(list(PERC_ID = 99))

df9 <- df9 %>% 
  replace_na(list(LEFT_RIGHT = 99))

#categorical in 4 categories

df10 <- df9 %>%
  data.frame() %>%
  select(PERC_ID, LEFT_RIGHT)

##rename

df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Strongly left leaning'] <- '1'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Fairly left leaning'] <- '2'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Slightly left leaning'] <- '3'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Neither left nor right leaning'] <- '4'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Slightly right leaning'] <- '5'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Fairly right leaning'] <- '6'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 'Strongly right leaning'] <- '7'

df10$PERC_ID[df10$PERC_ID == -3] <- 'Left leaning'
df10$PERC_ID[df10$PERC_ID == -2] <- 'Left leaning'
df10$PERC_ID[df10$PERC_ID == -1] <- 'Left leaning'
df10$PERC_ID[df10$PERC_ID == 0] <- 'Neither left nor right leaning'
df10$PERC_ID[df10$PERC_ID == 1] <- 'Right leaning'
df10$PERC_ID[df10$PERC_ID == 2] <- 'Right leaning'
df10$PERC_ID[df10$PERC_ID == 3] <- 'Right leaning'
df10$PERC_ID[df10$PERC_ID == 99] <- 'Not sure'

df10$LEFT_RIGHT[df10$LEFT_RIGHT == -3] <- 'Left leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == -2] <- 'Left leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == -1] <- 'Left leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 0] <- 'Neither left nor right leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 1] <- 'Right leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 2] <- 'Right leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 3] <- 'Right leaning'
df10$LEFT_RIGHT[df10$LEFT_RIGHT == 99] <- 'Not sure'

names(df10)[1] <- 'CAT_PERC_ID'
names(df10)[2] <- 'CAT_LEFT_RIGHT'

##need to also be as factor and reference group set

df10$CAT_PERC_ID <- as.factor(df10$CAT_PERC_ID)
df10$CAT_LEFT_RIGHT <- as.factor(df10$CAT_LEFT_RIGHT)

df10 <- df10 %>%
  mutate(
    CAT_PERC_ID = relevel(factor(CAT_PERC_ID, levels = 
                                 c("Left leaning", "Right leaning", 
                                   "Neither left nor right leaning", "Not sure"
                                 )), ref = "Neither left nor right leaning"
    )
  )

df10 <- df10 %>%
  mutate(
    CAT_LEFT_RIGHT = relevel(factor(CAT_LEFT_RIGHT, levels = 
                                 c("Left leaning", "Right leaning", 
                                   "Neither left nor right leaning", "Not sure"
                                 )), ref = "Neither left nor right leaning"
    )
  )

```

```{r creating dummy variables}

#creating dummy variables for categorical variables

df11 <- data %>%
  data.frame() %>%
  select(GENDER, EDUCATION)

#gender

df11 <- df11 %>%
  mutate(
    GENDER = relevel(factor(GENDER, levels = 
                                 c("Female", 
                                   "Male",
                                   "Non-binary / third gender",
                                   "Prefer not to say"
                                 )), ref = "Female"))

#education

df11 <- df11 %>%
 mutate(
    EDUCATION = relevel(factor(EDUCATION, levels = 
                              c("Postgraduate (e.g., M.Sc or Ph.D)",
                                "Undergraduate University (e.g., BA, B.Sc or B.Ed)",
                                "A level, or equivelent", "GCSE level, or equivelent",
                                "No formal qualifications",
                                "Other, please specify"
                              )), ref = "Postgraduate (e.g., M.Sc or Ph.D)"
    )
  )

```

```{r regulation trust}

#For this variable there is 1 missing piece of data, and 8 participants selected 'don't know' as their response. These 8 responses are changed to 99 in the data frame

df12 <- data %>%
  select(REG_TRUST_1)


df12 <- df12 %>%
  mutate(REG_TRUST_1 = c(1, 2, 3, 4, 5, 6, 7, 99, 99)[
    match(REG_TRUST_1, c("Strongly disagree", "Disagree", "Somewhat disagree",
                      "Neither agree nor disagree", "Somewhat agree", "Agree",
                      "Strongly agree", "", "Don't know"))
    ])

```

```{r recall variables}

#getting yes-no into correct, incorrect identify, incorrect non-identify

memory <- data %>%
  data.frame() %>%
  select(Condition, MEM_PAID, MEM_TAR)

memory$Condition <- as.numeric(memory$Condition)

memory$MEM_PAID[memory$MEM_PAID == 'Yes'] <- '1'
memory$MEM_PAID[memory$MEM_PAID == 'No'] <- '0'
memory$MEM_TAR[memory$MEM_TAR == 'Yes'] <- '1'
memory$MEM_TAR[memory$MEM_TAR == 'No'] <- '0'

memory$MEM_PAID <- as.numeric(memory$MEM_PAID)
memory$MEM_TAR <- as.numeric(memory$MEM_TAR)

memory$PAID_diff<-(memory$Condition-memory$MEM_PAID)

memory$PAID_diff[memory$PAID_diff == '0'] <- 'CORRECT'
memory$PAID_diff[memory$PAID_diff == '1'] <- 'NON_IDENTIFY'
memory$PAID_diff[memory$PAID_diff == '-1'] <- 'IDENTIFY'

memory$TAR_diff<-(memory$Condition-memory$MEM_TAR)

memory$TAR_diff[memory$TAR_diff == '0'] <- 'CORRECT'
memory$TAR_diff[memory$TAR_diff == '1'] <- 'NON_IDENTIFY'
memory$TAR_diff[memory$TAR_diff == '-1'] <- 'IDENTIFY'

memory$PAID_diff <- as.factor(memory$PAID_diff)
memory$TAR_diff <- as.factor(memory$TAR_diff)

memory <- memory %>%
  mutate(
    PAID_diff = relevel(factor(PAID_diff, levels = 
                                 c("NON_IDENTIFY", 
                                   "CORRECT",
                                   "IDENTIFY"
                                 )), ref = "NON_IDENTIFY"))

memory <- memory %>%
  mutate(
    TAR_diff = relevel(factor(TAR_diff, levels = 
                                 c("NON_IDENTIFY", 
                                   "CORRECT",
                                   "IDENTIFY"
                                 )), ref = "NON_IDENTIFY"))

```


```{r combining the final dataframe}

#binding the dataframe

final <- cbind(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12, memory)

#setting condition as a categorical dummy variable

final$Condition[final$Condition == '0'] <- 'control'
final$Condition[final$Condition == '1'] <- 'transparent'

final$Condition <- as.factor(final$Condition)

final <- final %>%
  mutate(
    Condition = relevel(factor(Condition, levels = 
                                 c("control", 
                                   "transparent"
                                 )), ref = "control"
    )
  )

```

## Renaming trust variables

```{r}

names(final)[1] <- 'TRUST_1' #orient_1_1
names(final)[2] <- 'MISTRUST_1'
names(final)[3] <- 'TRUST_2' #orient_1_3
names(final)[4] <- 'DISTRUST_1' #orient_1_4
names(final)[5] <- 'DISTRUST_2' #orient_1_5
names(final)[6] <- 'TRUST_3' #orient_2_1
names(final)[7] <- 'MISTRUST_2'
names(final)[8] <- 'DISTRUST_3' #orient_2_3
names(final)[9] <- 'TRUST_4' #orient_2_4
names(final)[10] <- 'DISTRUST_4' #orient_2_5
names(final)[12] <- 'MISTRUST_B_1'
names(final)[13] <- 'MISTRUST_B_2'
names(final)[15] <- 'MISTRUST_B_3'

names(final)[16] <- 'COMPTRUST_1'
names(final)[17] <- 'COMPDIS_1'
names(final)[18] <- 'COMPDIS_2'
names(final)[19] <- 'COMPTRUST_2'
names(final)[20] <- 'BENDIS_1'
names(final)[21] <- 'BENTRUST_1'
names(final)[22] <- 'BENDIS_2'
names(final)[23] <- 'BENTRUST_2'
names(final)[24] <- 'INTTRUST_1'
names(final)[25] <- 'INTDIS_1'
names(final)[26] <- 'INTDIS_2'
names(final)[27] <- 'INTTRUST_2'

names(final)[28] <- 'CREDIBLE'
names(final)[29] <- 'MANIPULATIVE'

```

## Mean-centering and adding in age

```{r}

df12 <- data %>%
  data.frame() %>%
  select(AGE)

df12 <- df12 %>%
  mutate(C_AGE = AGE)

final <- cbind(final, df12)

final$C_AGE <- final$C_AGE - mean(final$C_AGE)

```

## Reverse scoring distrust items

The code below is a function to reverse score all distrust items.
In other versions of analysis, distrust will form it's own dimension and scale and will not need to be reverse scored. For this reason, new variables are created for each item so both directions can be kept separate.

```{r reverse scoring distrust items}

reverse_code <- function(response) {
  # Define the mapping from original to reversed scores
  mapping <- c(1, 2, 3, 4, 5, 6, 7)
  names(mapping) <- c(7, 6, 5, 4, 3, 2, 1)
  
  # Use the response as a name to look up in the mapping
  return(as.numeric(names(mapping)[match(response, mapping)]))
}

#create new columns to keep the distrust dimension separate

final <- final %>%
  mutate(DISTRUST_1rev = DISTRUST_1,
         DISTRUST_2rev = DISTRUST_2,
         DISTRUST_3rev = DISTRUST_3,
         DISTRUST_4rev = DISTRUST_4,
         COMPDIS_1rev = COMPDIS_1,
         COMPDIS_2rev = COMPDIS_2,
         INTDIS_1rev = INTDIS_1,
         INTDIS_2rev = INTDIS_2,
         BENDIS_1rev = BENDIS_1,
         BENDIS_2rev = BENDIS_2)


final <- final %>%
  mutate(across(.cols = which(grepl("DIS", names(.)) & grepl("rev", names(.))),
    .fns = reverse_code))

```

## Mean scored items with trust and distrust on the same scale

```{r}

final <- final %>%
  rowwise() %>%
  mutate(trust_orientation = mean(c(TRUST_1, TRUST_2, TRUST_3, TRUST_4, DISTRUST_1rev, DISTRUST_2rev, DISTRUST_3rev, DISTRUST_4rev)))

final <- final %>%
  rowwise() %>%
  mutate(competence = mean(c(COMPTRUST_1, COMPTRUST_2, COMPDIS_1rev, COMPDIS_2rev)))

final <- final %>%
  rowwise() %>%
  mutate(integrity = mean(c(INTTRUST_1, INTTRUST_2, INTDIS_1rev, INTDIS_2rev)))

final <- final %>%
  rowwise() %>%
  mutate(benevolence = mean(c(BENTRUST_1, BENTRUST_2, BENDIS_1rev, BENDIS_2rev)))

#transparency items mean scored

final <- final %>%
  rowwise() %>%
  mutate(TRANSPARENT = mean(c(AD_TRUST_4, AD_TRUST_5)))

#social media trust mean scored

final <- final %>%
  rowwise() %>%
  mutate(SMtrust = mean(c(SM_TRUST_1, SM_TRUST_2)))

#total trustworthiness mean scored

final <- final %>%
  rowwise() %>%
  mutate(trustw_total = mean(c(competence, integrity, benevolence)))

```


## Make variables to go in model on a scale of -3 to +3

```{R changing scale of variables}

#subtract_four <- function(df, cols) {
#  df %>%
#    mutate(across(all_of(cols), ~ . - 4))
#}

#final <- subtract_four(final, c("CREDIBLE", "MANIPULATIVE", "trust_orientation", "competence", "integrity", "benevolence", "trustw_total"))

```

## Extra dataframe for regulation questions

For regulation trust, there are 8 NA values of people who said 'don't know'. As there are so few, these are now changed to a value '4' to retain all other observations in the final analysis. However, models need to be checked with and without these 8 observations to ensure the inclusion/exclusion of these don't know options do not impact the model estimates.

```{r}

#Create a dataframe with the don't know values kept at 99 for exclusion

regulation_ex <- final %>%
  select(everything())
  
#alter the existing dataframe so 99 becomes 4

final <- final %>%
  mutate(REG_TRUST_1 = ifelse(REG_TRUST_1 == 99, 4, REG_TRUST_1))

```

## Clean up the environment

```{r remove unecessary df from environment}



```

## Create recall data frame 

```{r recall dataframe}

df_recall <- final %>%
  data.frame() %>%
  select(Condition, C_AGE, GENDER, EDUCATION, AGREE, CAT_LEFT_RIGHT, PAID_diff, TAR_diff, MANIPULATIVE, DATA_ACCEPT, SMtrust, REG_TRUST_1, trust_orientation, competence, integrity, benevolence, trustw_total, CREDIBLE)

df_recall <- df_recall %>%
  subset(Condition == "transparent")

df_recall$Condition <- droplevels(df_recall$Condition)
df_recall$PAID_diff <- droplevels(df_recall$PAID_diff)
df_recall$TAR_diff <- droplevels(df_recall$TAR_diff)

```

## Bivariate graphs

```{r}

plot <- ggplot(df_recall, aes(x = PAID_diff, y = MANIPULATIVE)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  ylim(-3, 3)


plot <- ggplot(df_recall, aes(x = PAID_diff, y = MANIPULATIVE, group = 1)) + # Add 'group = 1' to ensure a single group for line
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "blue") +
  stat_summary(fun.y = mean, geom = "point", size = 3, color = "red") + # Add points for means
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "green")  # Draw a line connecting means
  

plot <- ggplot(df_recall, aes(x = PAID_diff, y = MANIPULATIVE, group = 1)) +
  geom_jitter(size = 0.8, color = "black", width = 0.2, height = 0.2, alpha = 0.2) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "black") + 
  stat_summary(fun.y = mean, geom = "point", size = 1, color = "sienna2") +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "sienna2") +
  ylim(-3, 3) +
  labs( 
       x = "", 
       y = "Manipulativeness score") +
  theme_minimal() + 
  theme(text = element_text(size = 10)) +
  scale_x_discrete(labels = c("NON_IDENTIFY" = "Did not remember", "CORRECT" = "Correctly remembered"))

plot2 <- ggplot(df_recall, aes(x = PAID_diff, y = CREDIBLE, group = 1)) +
  geom_jitter(size = 0.8, color = "black", width = 0.2, height = 0.2, alpha = 0.2) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "black") + 
  stat_summary(fun.y = mean, geom = "point", size = 1, color = "sienna2") +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "sienna2") +
  ylim(-3, 3) +
  labs( 
       x = "", 
       y = "Credibility score") +
  theme_minimal() + 
  theme(text = element_text(size = 10)) +
  scale_x_discrete(labels = c("NON_IDENTIFY" = "Did not remember", "CORRECT" = "Correctly remembered")) 

plot3 <- ggplot(df_recall, aes(x = PAID_diff, y = trustw_total, group = 1)) +
  geom_jitter(size = 0.8, color = "black", width = 0.2, height = 0.2, alpha = 0.2) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "black") + 
  stat_summary(fun.y = mean, geom = "point", size = 1, color = "sienna2") +
  stat_summary(fun.y = mean, geom = "line", aes(group = 1), color = "sienna2") +
  ylim(-3, 3) +
  labs( 
       x = "", 
       y = "Trustworthiness score") +
  theme_minimal() + 
  theme(text = element_text(size = 10)) +
  scale_x_discrete(labels = c("NON_IDENTIFY" = "Did not remember", "CORRECT" = "Correctly remembered")) 

plot 

plot2

plot3

```






